Making all equalities equal

### 2021-09-22 paper.lagda.tex
got leibniz equality from equalities

      module _ {_≣_ : ≣-Type'} where
        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type (ℓ-max a ℓ)
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y)
          → IsEquality₃ _≣_
        sym-Equality₃ ≡-≡-≣ = eq (let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = transport (sym α₁) ≡-≡-≣
          in transport α₁ (sym α₂))
\end{code}

>>>>

      module _ {_≣_ : ≣-Type'} where
        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type (ℓ-max a ℓ)
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y)
          → IsEquality₃ _≣_
        sym-Equality₃ ≡-≡-≣ = eq (let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = transport (sym α₁) ≡-≡-≣
          in transport α₁ (sym α₂))

module _ {A : Set} where
  open Equalities {ℓ-zero} {ℓ-suc ℓ-zero} {A}

  _≡p₁_ : A → A → Set₁
  x ≡p₁ y = x ≡p y

  _ = ≡p-IsEquality
  instance
    ≡p₁-isEquality : IsEquality _≡p₁_
    ≡p₁-isEquality = eq λ {x y} → (sym λ i → let
      α : Type₁
      α = p-c {ℓ-zero} {A} {x = x} {y = y} i
      in α)

  leibniz : IsEquality  (_≐_ {A})
  leibniz =
    IsEquality₂.isEquality (eq λ {x y} → FinalEquality.≐≡≡ {_} {x} {y})

\end{code}
